\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=.9cm,tmargin=1.2cm]{geometry}
\usepackage[none]{hyphenat}
\usepackage{lipsum,xcolor,relsize,xspace,hyperref}

\setlength{\parindent}{0pt}

%\colorlet{hl}{black!70}
\definecolor{hl}{HTML}{800020}

\newcommand\hone{\fontfamily{phv}\fontseries{sluc}\fontsize{14}{16}\selectfont }
\newcommand\institute{\fontfamily{phv}\fontseries{bx}\fontsize{11}{14}\selectfont }
\newcommand\qualification{\fontfamily{phv}\fontseries{m}\fontshape{sl}\fontsize{10}{11}\selectfont }
\newcommand\stdate{\fontfamily{phv}\fontseries{m}\fontshape{sc}\fontsize{10}{11}\selectfont }
\newcommand\grade{\fontfamily{phv}\fontseries{sluc}\fontsize{10}{11}\selectfont\color{hl} }
\newcommand\info{\fontfamily{phv}\fontseries{sluc}\fontsize{10}{11}\selectfont\color{hl} }
\newcommand\boldinfo{\fontfamily{phv}\fontseries{b}\fontsize{10}{11}\selectfont\color{hl} }
\newcommand\itinfo{\fontfamily{phv}\itshape\fontsize{10}{11}\selectfont\color{hl} }

\newcommand\dash{ {\large\bf --} }
\newcommand\dateword{\hspace{1px}\fontfamily{phv}\fontseries{m}\fontshape{n}\fontsize{9}{10}\selectfont}
\newcommand\cpp{{C\nolinebreak[4]\hspace{-.15em}\raisebox{.4ex}{\relsize{-3}\bf +\hspace{-.15em}+}}\xspace}

\newcommand\skill\institute
\newcommand\planguage\desc%\stdate
\newcommand\boldplanguage{\fontfamily{phv}\fontseries{b}\fontsize{10}{11}\selectfont }
\newcommand\desc{\fontfamily{phv}\fontseries{sluc}\fontsize{10}{11}\selectfont }
\newcommand\module\planguage%{\fontfamily{phv}\fontseries{m}\fontshape{sl}\fontsize{10}{11}\selectfont }
\newcommand\referee{\fontfamily{phv}\fontseries{bx}\fontsize{10}{11}\selectfont }
\newcommand\sep{\,{\color{black}\bf\textbar}\,}
\newcommand\referenceonrequest{%
  \hrule\vspace{.7em}
  {\qualification References available on request.}
}
\newcommand\hl[1]{{\color{hl}#1}}

\begin{document}
\thispagestyle{empty}

\begin{minipage}{\textwidth}

   %TOP PANEL (TITLE)
  \begin{minipage}[t]{0.7\textwidth}
    {\fontfamily{phv}\fontseries{ubuc}\fontsize{22}{25}\selectfont%
      HARRY COOKE
      \fontfamily{phv}\fontseries{sluc}\fontsize{18}{20}\selectfont\color{hl}
      \hspace{1pt}PhD
    }\\[.2em]
    {\fontfamily{phv}\fontseries{sluc}\fontsize{12}{14}\selectfont\color{hl}%
      Software engineer\sep Data scientist\sep Particle physicist
    }
  \end{minipage}\vspace{-.2em}%
  \begin{minipage}[t]{0.3\textwidth}
    \vspace{-1.65em}
    \raggedleft\info
      \vspace{-.3em}
      hcooke006@aol.com \\[0.1em]
      +44 7528 694569 \\[0.1em]
      \href{https://github.com/Hazza4569}{github.com/Hazza4569}
  \end{minipage}

\end{minipage}

\vspace{0.5em}
%\hrule
\vspace{0.5em}

\begin{minipage}[t]{0.64\textwidth}
  % LEFT COLUMN
  \newcommand\intersectionspacing{0.8em}
  \newcommand\intersegmentspacing{-.5em}
  % ==== EXPERIENCE ======
  {\hone Experience} \vspace{0.25em} \hrule \vspace{0.5em}

  {\institute Acturis} \dash
  { \qualification Technical Business Analyst}\\
  {\stdate {\dateword MAY} 2024 - \dateword{PRESENT}}\\
  {\info Working with clients to build and maintain insurance products}\\[\intersegmentspacing]

  {\institute University of Birmingham} \dash
  { \qualification Postgraduate Teaching Assistant}\\
  {\stdate {\dateword OCTOBER} 2019 - \dateword{MARCH} 2023}\\
  {\info Teaching in undergraduate computing and physics labs during PhD}\\[\intersegmentspacing]

%  {\institute CERN} \dash
%  { \qualification Summer Studentship}\\
%  {\stdate {\dateword JUNE - AUGUST} 2018}\\
%  {\info Developing a monitoring system for AMC13 modules in the CMS detector}\\
%  {\info \url{http://cdlib.cern.ch/record/2640969}}\\[\intersegmentspacing]
%
  \vspace{\intersectionspacing}

  % ===== EDUCATION =====
  {\hone Education} \vspace{0.5em} \hrule \vspace{0.5em}

  {\institute University of Birmingham}\\
  {\stdate 2019 - 2023} \dash
  { \qualification PhD Particle Physics}\\
  {\info%
    Searching for rare Standard Model interactions with the
    ATLAS collaboration
  }\\
  {\info%
    Statistical analysis, machine learning, programming in \cpp and Python
  }\\[\intersegmentspacing]

  {\institute University of Birmingham}\\
  {\stdate 2015 - 2019} \dash
  { \qualification%
    MSci Physics with Particle Physics and Cosmology \\
    Class I, Cum Laude
  }\\
  {\info Graduated first in year for experimental physics}\\
  {\info Awarded Bloodworth Prize (Y3) and Moreton Prize (Y4) for academic excellence}
  {\info and Tessella Prize for most innovative use of software in a Y4 project}
  \\[\intersegmentspacing]

  {\institute Hereford Sixth Form College}\\
  {\stdate 2013 - 2015} \dash
  { \qualification A-Levels:
  %{\grade
  A*s in physics, maths, further maths, computing
  }

  \vspace{\intersectionspacing}

  % ==== TECHNICAL SKILLS ======
  {\hone Technical Skills} \vspace{0.5em} \hrule \vspace{0.5em}

  % > PROGRAMMING
  {\skill Software development}\\
  % > Primary languages
  {\info 10 years of experience and competent in multiple programming languages:}\\
  {\boldplanguage \cpp}\dash
  {\desc%
    Daily use throughout PhD for data analysis and algorithm design, working
    with large software frameworks. 8 years of experience.
  }\\
  {\boldplanguage Python}\dash
  {\desc%
    Developed internal tools to automate common processes at Acturis.
    Used for scripting and data visualisation in PhD and for larger personal
    projects. Taught to Y3 undergraduate students. 7 years of experience.
  }\\
  {\boldplanguage JavaScript {\dateword (HTML, CSS)}}\dash
  {\desc%
    Built monitoring and visualisation tools for use with detector hardware.
    Some small personal web projects. 6 years of experience.
  }\\
  {\boldplanguage SQL}\dash
  {\desc%
    Used extensively in role at Acturis to maintain databases for client
    information and product configuration. 6 months of experience.
  }\\
  % > Additional languages
  {\info Some experience with many more languages, including}\\
  {\planguage%
    Bash, Ruby, Java, Go, Rust, Kotlin, Matlab, Maple, Julia, XSLT, XPath
  }\\[\intersegmentspacing]

  % > DATA ANALYSIS
  {\skill Data analysis}\\
  {\info Experienced with a number of analysis techniques:}\\
  {\desc%
    Analysis performed during the PhD required use and understanding of
    \qualification
    machine learning techniques, likelihood model building, maximum likelihood
    estimation, treatment of systematic and statistical uncertainties,
    hypothesis testing,
    \desc
    and more.
    Received formal training in statistical methods during undergraduate degree
    and in a postgraduate course.
  }\\[\intersegmentspacing]

  % > QUALITY ASSURANCE
  {\skill Quality assurance}\\
  {\info Always ensure the highest build quality through extensive testing:}\\
  {\desc%
    For each change built at Acturis, write detailed test packs ensuring new
    and existing functionality works as expected. Either conduct testing
    personally or coordinate with internal teams to ensure 100\% pass rate on
    all tests. Built and shared tools to automate common testing processes.
  }\\[\intersegmentspacing]

  % > Misc
  {\skill Miscellaneous}\\
  {\desc Experienced with \hl{version-control software}, see a selection of projects on my
    \href{https://github.com/Hazza4569}{\color{hl}\underline{GitHub page}}.
    Adept in operation of \hl{unix-based systems} and \hl{Windows}, for both work and personal use.
    Proficient in writing and typesetting of documents, particularly with
    {\LaTeX} -- created the official University of Birmingham
    \href{https://www.overleaf.com/edu/bham#templates}
    {\color{hl}\underline{overleaf templates}}.
  }\\

  \vspace{-.2em}
  \referenceonrequest

\end{minipage}%
\hfill
%\vrule
%\hfill
\begin{minipage}[t]{0.339\textwidth}
  \newcommand\interskillspacing{.3em}

  %RIGHT COLUMN
  % ===== Transferable skills =====
  {\hone Transferable Skills} \vspace{0.5em} \hrule \vspace{0.5em}
  {\skill Project management}\\
  {\desc
    Independently planned and performed a 2.5-year-long physics analysis.
    Involved long-term planning and prioritisation of tasks to ensure that the analysis
    was completed within the timeline of the PhD.
  }\\[\interskillspacing]
  {\skill Client Relations}\\
  {\desc
    Worked directly with multiple clients in role at Acturis to ensure builds
    are delivered to requirements and defects are investigated and resolved
    promptly. Product owner for one client, acting as first point of contact
    for issues or requests.
  }\\[\interskillspacing]
  {\skill Teamwork and communication}\\
  {\desc
    Collaborated on many projects with colleagues within the University
    and internationally. Worked on an analysis with a team of
    $\sim$10 physicists to attain a world-leading result.
    In the L1Calo operations team, took week-long 24/7 on-call shifts to
    ensure continuous running of the ATLAS experiment.
    Communicate frequently with internal teams at Acturis to delegate
    tasks and ensure that projects are delivered on time and to high quality.
  }\\[\interskillspacing]
  {\skill Time management}\\
  {\desc
    Worked on multiple concurrent projects during the PhD and learned to
    effectively split time between tasks, whilst also scheduling individual work
    time around meetings and other commitments. Have applied this experience to
    manage many simultaneous projects at Acturis.
  }\\[\interskillspacing]
  {\skill Leadership}\\
  {\desc
    As an undergraduate, led 14 students for a 3-month project, producing a
    90-page document on design of high-energy particle detectors.
    Responsibilities included dividing and delegating tasks amongst small teams,
    setting deadlines, and organising and chairing regular meetings.
  }\\[\interskillspacing]
  {\skill Problem solving} \\
  {\desc
    Demonstrated through research in deriving solutions to mathematical problems, implementing
    code to analyse very large datasets or simulate systems, and optimising
    an analysis to best extract a result from data.
  }\\
  \vspace{0.5em}

  % ==== PERSONAL INTERESTS ======
  {\hone Personal Interests} \vspace{0.5em} \hrule \vspace{0.5em}
  {\desc%
    Enjoy playing tennis and 5-a-side football.  Founder and first president of
    the University of Birmingham Benchball Society.  Enjoy working with
    computers, having built a custom PC for work, gaming, and more.
  }

\end{minipage}

%\vspace{1.2em}
%\hrule

\end{document}
